\documentclass[a4paper, 11pt]{article}
\usepackage{fancyhdr}
\usepackage{titlesec}

\pagestyle{fancy}

\lhead{}
\chead{}
\rhead{}
\lfoot{Prepared by Siddharth Kannan}
\cfoot{}
\rfoot{}

\title{Minutes of the Meeting dated 10th August, 2014}
\author{meeting of the web subdivision}

\begin{document}

\maketitle

\section{Attendees}

Web Team only.

\titlerule

\begin{itemize}
\item{Karan Gupta}
\item{Siddharth Kannan}
\item{Vaibhav Gavhale}
\end{itemize}

Discussion with Punit Pal after meeting. He has expressed his willingness to work on the website. He will be working with Siddharth Kannan on the PHP part of the website.

\section{Things required from the design team}
\begin{itemize}
\item{High Resolution Photos of all the events till now}
\item{Redesigned LOGO}
\end{itemize}

\section{Things required from the content team}

\begin{itemize}
\item{Updated articles related to the Energy sector}
\item{Text to be filled in the ``About Us'' and the ``Mission'' sub sections in the website. Also, the PDF version of the Brochure, so that it can be linked on the website.}
\item{Descriptions and Stuff about the speakers at the three events}
\end{itemize}

\section{Plan for the website}

\begin{itemize}
\item{Overall layout will not change much}
\item{Home page will have a slider at the bottom with the articles sliding through}
\item{Create a mailing list using PHP, for users who wish to register for the newsletter}
\item{Create a Form for Chapter Registration}
\item{Remove members who are not there anymore with YEC from the About Us page}
\end{itemize}

\section{People working on the website}

\subsection{Karan Gupta}

He will be working on the CSS of the website.

\subsection{Punit Pal and Siddharth Kannan}

We will be working on the PHP related stuff, and also, on putting the whole website together.

\end{document}
